The Galactic Midplane is Not a Plane: Implications for dynamical analysis with {\em Gaia} data and beyond

### 2019-04-22 paper/ms.tex
Add velocity epicyclic calc

We will check these formulae against numerical tests next.

>>>>

A similarly rough argument can be made to arrive at the following formulae for
the impact of velocity offsets on the actions,
\beq\label{eq:actions_epi_error}
\begin{split}
\frac{\Delta L_z}{L_z} &= \frac{\Delta v_{\phi}}{v_c} \\
\frac{\Delta J_r}{J_r} &= \frac{\Delta v_R}{v_{R,\text{max}}} \\
\frac{\Delta J_z}{J_z} &= \frac{\Delta v_z}{v_{z,\text{max}}}\text{,}
\end{split}
\eeq
where $v_{R,\text{max}}$ and $v_{z,\text{max}}$ are the maximum radial and
vertical velocities of the orbit, respectively.

We will check the formulae for the midplane offset against numerical tests
next. The effect of velocity offsets on actions is deferred to future work, as
we discuss in Section~\ref{ssec:lsr_var}.
